Fail Faster

### 2025-03-21 paper/paper.tex
nit

\subsection{Benchmarking Generator Speed}
\label{subsection:benchmarking}
To answer \textbf{RQ1}, we microbenchmark generators, comparing generators in \camlname to semantically identical ones in \bq,
and generators in \scalaname to those in ScalaCheck.
 We vary the choice of \rand in our \camlname generators, using both \bq's default
\texttt{splittable\_random} and \csplitmix, as discussed
in \secref{subsection:faster-rng}. Our test cases consist of generators for boolean lists, binary search trees (BST), and simply
typed lambda calculus (STLC) terms. We implement generators for these benchmarks
variety of \textit{strategies}, varying in structure and
sophistication.

@@

The runtime of \camlname generators across different input sizes is summarized in \figref{fig:time}.
Our \camlname type-derived BST generator achieves speedups ranging from $1.08-1.29\times$, which increase
dramatically, to $6.13-9.65\times$, when combined with \csplitmix. The insertion-based BST generator sees
$1.13-1.21\times$ speedups with staging alone, and $4.32-5.36\times$ when also
using \csplitmix. The single-pass BST generator benefits more significantly from
staging, with speedups of $2.31-2.34\times$, rising to $8.61-8.95\times$ when combined with
\csplitmix. We attribute the difference in performance speedup to the fact that
BST strategies rely on relatively few calls to generator combinator functions,
but sample extensively from the \rand; notably, single-pass BST, which uses the largest
number of calls to generator combinators, also sees the greatest benefit from staging. \tr{Call this out earlier? Unless we have the fancy plot.}

>>>>

\subsection{Benchmarking Generator Speed}
\label{subsection:benchmarking}
To answer \textbf{RQ1}, we microbenchmark generators, comparing generators in \camlname to semantically identical ones in \bq,
and generators in \scalaname to those in ScalaCheck.
 We vary the choice of \rand in our \camlname generators, using both \bq's default
\texttt{splittable\_random} and \csplitmix, as discussed
in \secref{subsection:faster-rng}. Our test cases consist of generators for boolean lists, binary search trees (BST), and simply
typed lambda calculus (STLC) terms. We implement generators for these benchmarks using a
variety of \textit{strategies} varying in structure and
sophistication.

@@

The runtime of \camlname generators across different input sizes is summarized in \figref{fig:time}.
Our \camlname type-derived BST generator achieves speedups ranging from $1.08-1.29\times$, which increase
dramatically, to $6.13-9.65\times$, when combined with \csplitmix. The insertion-based BST generator sees
$1.13-1.21\times$ speedups with staging alone, and $4.32-5.36\times$ when also
using \csplitmix. The single-pass BST generator benefits more from
staging, with speedups of $2.31-2.34\times$, rising to $8.61-8.95\times$ when combined with
\csplitmix. We attribute the difference in performance speedup to the fact that
BST strategies rely on relatively few calls to generator combinator functions,
but sample extensively from the \rand; notably, single-pass BST, which uses the largest
number of calls to generator combinators, also sees the greatest benefit from staging. \tr{Call this out earlier? Unless we have the fancy plot.}
